---
title: "Covid Intervention Results"
author: "Joey Heffner"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

# Setup
To run this analysis script you'll have to have the following packages installed (make sure tidyverse is updated): 

`here`, `tidyverse`, `knitr`, `kableExtra`, `lsr`, `broom.mixed`, `AICcmodavg`, `cowplot`, `ggrepel`

The order of this Markdown will follow the order of the manuscript. Currently, the sections are broken into: 

- Data
- Pre-figure 1 statistics
- Figure 1a
- Figure 1b
- Figure 2
- Figure 3

```{r setup, include=FALSE}
# Knitr options
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE, message = FALSE)

# Save plots or not
save_plots <- FALSE # plots already saved

# Libraries
library(here)         # relative paths
library(tidyverse)    # tidy functions
library(knitr)        # knit functions
library(kableExtra)   # extra markdown functions
library(lsr)          # cohenD()
library(broom.mixed)  # tidy() 
library(AICcmodavg)   # predictSE()
library(cowplot)      # plot_grid()
library(ggrepel)      # geom_text_repel
```

# Data
Below you can see a snippet of the data. The columns of the data refer to: 

- `sub`: unique subject identifier
- `intervention`: `fear` intervention or `altruism` intervention
- `valence`: unpleasant (-) or pleasant (+) rating of the intervention (-250 to +250)
- `arousal`: low (-) or high (+) arousal rating of the intervention (-250 to + 250)
- `willingness`: self-report rating of willingness to self-isolate (0 - not at all), (100 - completely) 
- `change`: self-report change in willingness to self-isolate after reading intervention (0 - no change), (100 - a lot of change)
- `stay_home`: self-report baseline for self-isolation ("I stayed home; 0 - not at all, 100 - all the time)

The two intervention prompts are shown below: 

#### Fear
<center>"The coronavirus is coming for you. When it does, your healthcare system will be overwhelmed. Your fellow citizens will be turned away at the hospital doors. Exhausted healthcare workers will break down. Millions will die. The only way to prevent this crisis is social distancing today."</center>

#### Altruism
<center>"Help save our most vulnerable. Together, we can stop the coronavirus. Everyone's actions count, every single person can help to slow the crisis. We have the tools to solve this problem. Together, by self isolating we can save millions of lives."</center>

#### Questions
The three questions participants were asked after each intervention are shown below: 

1. How does this statement make you feel? (`valence` + `arousal`)
2. On a scale from 0 (not at all) to 100 (completely), how willing are you to self-isolate? (`willingness`)
3. On a scale from 0 (no change) to 100 (a lot of change), how much does the previous statement change your willingness to self-isolate? (`change`)

```{r read_data}
# Specify relative pathing
dir_analysis <- here() # should be where analysis script is stored
dir_parent <- dir_analysis %>% str_remove("/Analysis")
dir_data <- paste0(dir_parent, "/Data")
dir_graphs <- paste0(dir_parent, "/Graphs")

# Load data
df <- read_csv(paste0(dir_data, "/covid_intervention.csv"))

# Glimpse of data
head(df) %>%
  kable(caption = "Data glimpse") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Pre-figure 1 statistics
Shows the following statistics: 

- average stay at home value (`avg_stay_home`)
- descriptives for difference measures (`avg_diff` = `willingness` - `stay_home`)
- one-sample t-tests comparing difference measure to 0

```{r pre_fig1}
## Average stay_home behavior
stay_home <- df %>% 
  select(sub, stay_home) %>% 
  unique() %>% # unique value per sub
  summarise(avg_stay_home = mean(stay_home))

stay_home %>% 
  kable(caption = "Stay_Home Descriptive") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) 

## Difference measures
difference <- df %>%
  mutate(delta = willingness - stay_home)
  
# Difference descriptives
difference_avg <- difference %>% 
  group_by(intervention) %>%
  summarise(avg_diff = mean(delta), sd_diff = sd(delta), N = n())

difference_avg %>%
  kable(caption = "Difference descriptives") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# Difference statistics
diff_t1 <- t.test(difference %>% filter(intervention == "fear") %>% .$delta, mu = 0)
d_t1 <- cohensD(difference %>% filter(intervention == "fear") %>% .$delta, mu = 0)

t1_table <- data.frame(row.names = "fear",
                       t = round(diff_t1$statistic, 2), 
                       df = diff_t1$parameter, 
                       p = format(round(diff_t1$p.value, 3), nsmall = 3), 
                       d = round(d_t1, 2),
                       mu = diff_t1$null.value)

diff_t2 <- t.test(difference %>% filter(intervention == "altruism") %>% .$delta, mu = 0)
d_t2 <- cohensD(difference %>% filter(intervention == "altruism") %>% .$delta, mu = 0)

t2_table <- data.frame(row.names = "altruism",
                       t = round(diff_t2$statistic, 2), 
                       df = diff_t2$parameter, 
                       p = format(round(diff_t2$p.value, 3), nsmall = 3), 
                       d = round(d_t2, 2),
                       mu = diff_t2$null.value)

t_tables <- rbind(t1_table, t2_table)
t_tables %>%
  kable(caption = "One-sample t-tests") %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Figure 1a - Self-isolation behavior after reading each intervention
- Figure 1a graph
- Figure 1a descriptives
- Figure 1a statistics

```{r fig1a}
## Figure 1a - Overall intervention 
fig1a_data <- df %>%
  select(sub, intervention, willingness, change) %>% 
  pivot_longer(cols = c(willingness, change), names_to = "question", values_to = "value") %>% 
  mutate(question = fct_relevel(question, "willingness", "change")) %>%
  group_by(intervention, question) %>%
  summarise(Mean = mean(value), SD = sd(value), N = n(), SE = SD/sqrt(N)) %>%
  mutate(lwr = Mean - qt(1 - (0.05 / 2), N - 1) * SE,
         upr = Mean + qt(1 - (0.05 / 2), N - 1) * SE)

# Aesthetics 
intervention_colors <- c("#66c2a5", "#f46d43") # Altruism, Fear

fig1a_plot <- ggplot(fig1a_data, aes(x = question, y = Mean, fill = intervention)) + 
  geom_bar(stat = "identity", position = position_dodge(.9)) + 
  geom_errorbar(aes(ymin = lwr, ymax = upr), position = position_dodge(.9), width = .1) +
  scale_fill_manual(values = intervention_colors) + 
  scale_y_continuous(name = NULL, limits = c(0, 100)) + 
  xlab("Self-Isolation Behavior") + 
  facet_wrap(~question, scales = "free", 
             strip.position = "left", 
             labeller = as_labeller(c(willingness = "Rating", change = "Rating"))) + 
  theme_bw() +
  theme(axis.text = element_text(size = rel(1.25)),
        axis.title = element_text(size = rel(1.5)), 
        legend.text = element_text(size = rel(1.25)), 
        legend.title = element_text(size = rel(1.5)), 
        strip.text = element_text(size = rel(1.5)), 
        strip.background = element_blank(),
        strip.placement = "outside")
fig1a_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig1a.pdf"), plot = fig1a_plot, width = 6, height = 6)
}

# Figure 1a descriptives
fig1a_data %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) 

# Figure 1a statistics
t1_test <- t.test(willingness ~ intervention, paired = TRUE, data = df) # cleaner paired t-test code
# t.test(df$willingness[df$intervention == "fear"], df$willingness[df$intervention == "altruism"], paired = TRUE) # same results
t1_table <- data.frame(row.names = "willingness",
                       t = round(t1_test$statistic, 2), 
                       df = t1_test$parameter, 
                       p = format(round(t1_test$p.value, 3), nsmall = 3))

t2_test <- t.test(change ~ intervention, paired = TRUE, data = df) 
t2_table <- data.frame(row.names = "change",
                       t = round(t2_test$statistic, 2), 
                       df = t2_test$parameter, 
                       p = format(round(t2_test$p.value, 3), nsmall = 3))

t_tables <- rbind(t1_table, t2_table)
t_tables %>%
  kable(caption = "Paired-sample t-tests") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Figure 1b - Emotional experiences after interventions
- Figure 1b graph
- Figure 1b descriptives
- Figure 1b statistics

```{r fig1b}
## Figure 1b - Emotional experiences
# Average emotions
fig1b_data <- df %>% 
  group_by(intervention) %>%
  dplyr::summarise(meanValence = mean(valence), meanArousal = mean(arousal),
                   sdValence = sd(valence), sdArousal = sd(arousal), N = n(), 
                   seValence = sdValence / sqrt(N), seArousal = sdArousal / sqrt(N)) %>%
  mutate(ciLowerValence = meanValence - qt(1 - (0.05 / 2), N - 1) * seValence,
         ciUpperValence = meanValence + qt(1 - (0.05 / 2), N - 1) * seValence, 
         ciLowerArousal = meanArousal - qt(1 - (0.05 / 2), N - 1) * seArousal,
         ciUpperArousal = meanArousal + qt(1 - (0.05 / 2), N - 1) * seArousal)

fig1b_plot <- ggplot(df, aes(x = valence, y = arousal, color = intervention)) + geom_point(alpha = .1) + # all data points
  geom_point(data = fig1b_data, aes(x = meanValence, y = meanArousal, color = intervention), size = 1) + # averages
  geom_errorbar(data = fig1b_data, aes(x = meanValence, y = meanArousal, ymin = ciLowerArousal, ymax = ciUpperArousal), width = 0) + # CIs
  geom_errorbarh(data = fig1b_data, aes(x = NULL, y = meanArousal, xmin = ciLowerValence, xmax = ciUpperValence), height = 0) + # CIs
  geom_text_repel(data = fig1b_data, aes(x = meanValence, y = meanArousal, color = intervention, label = intervention), 
                  segment.colour = NA, point.padding = .3, show.legend = FALSE, size = 8, nudge_y = 1, direction = "y") + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) +
  coord_fixed() +
  scale_color_manual(values = intervention_colors) + 
  scale_y_continuous(name = "Arousal", limits = c(-250, 250), breaks = seq(-200, 200, by = 100)) +
  scale_x_continuous(name = "Valence", limits = c(-250, 250), breaks = seq(-200, 200, by = 100)) +
  theme_bw() + 
  theme(axis.text = element_text(size = rel(1.25)), 
        axis.title = element_text(size = rel(1.5)), 
        legend.text = element_text(size = rel(1.25)), 
        legend.title = element_text(size = rel(1.5)),
        legend.position = "none", 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
fig1b_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig1b.pdf"), plot = fig1b_plot, width = 6, height = 6)
}

# Figure 1b descriptives
fig1b_data %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

# Figure 1b statistics
t1_test <- t.test(df$arousal[df$intervention == "fear"], df$arousal[df$intervention == "altruism"], paired = TRUE, data = df)
t1_d <- cohensD(x = df$arousal[df$intervention == "fear"], y = df$arousal[df$intervention == "altruism"], method = "paired") # less clean but works with cohenD function
t1_table <- data.frame(row.names = "arousal",
                       t = round(t1_test$statistic, 2), 
                       df = t1_test$parameter, 
                       p = format(round(t1_test$p.value, 3), nsmall = 3), 
                       d = round(t1_d, 2))

t2_test <- t.test(df$valence[df$intervention == "fear"], df$valence[df$intervention == "altruism"], paired = TRUE, data = df)
t2_d <- cohensD(x = df$valence[df$intervention == "fear"], y = df$valence[df$intervention == "altruism"], method = "paired")
t2_table <- data.frame(row.names = "valence",
                       t = round(t2_test$statistic, 2), 
                       df = t2_test$parameter, 
                       p = format(round(t2_test$p.value, 3), nsmall = 3), 
                       d = round(t2_d, 2))

t3_test <- t.test(abs(df$valence[df$intervention == "fear"]), abs(df$valence[df$intervention == "altruism"]), paired = TRUE, data = df)
t3_d <- cohensD(x = abs(df$valence[df$intervention == "fear"]), y = abs(df$valence[df$intervention == "altruism"]), method = "paired")
t3_table <- data.frame(row.names = "abs(valence)",
                       t = round(t3_test$statistic, 2), 
                       df = t3_test$parameter, 
                       p = format(round(t3_test$p.value, 3), nsmall = 3), 
                       d = round(t3_d, 2))

t_tables <- rbind(t1_table, t2_table, t3_table)
t_tables %>%
  kable(caption = "Paired-sample t-tests") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Figure 2 - Emotional experience predicts reported willingness to self-isolate after altruistic intervention
- Figure 2 graph
- Figure 2 descriptives
- Figure 2 statistics

```{r fig2}
## Figure 2 data
fig2_data <- df %>%
  mutate(willingness_scale = as.numeric(scale(willingness)), 
         change_scale = as.numeric(scale(change)), 
         valence_scale = as.numeric(scale(valence, center = F)), # scale but not mean-center (0 = neutral)
         arousal_scale = as.numeric(scale(arousal, center = F)), # scale but not mean-center (0 = neutral)
         intervention = fct_relevel(intervention, "fear", "altruism")) # reference point fear

## Figure 2 plot
fig2_theme <- theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text = element_text(size = rel(1.5)), 
        axis.title = element_text(size = rel(1.75)), 
        legend.text = element_text(size = rel(1.5)), 
        legend.title = element_text(size = rel(1.75)))

range_valence <- range(fig2_data$valence_scale)
range_arousal <- range(fig2_data$arousal_scale)
xRange1 <- seq(range_valence[1], range_valence[2], by = .1)
xRange2 <- seq(range_arousal[1], range_arousal[2], by = .1)
xRange3 <- c("altruism", "fear")

v_pred <- with(fig2_data, expand.grid(valence_scale = xRange1, arousal_scale = 0, intervention = xRange3))
a_pred <- with(fig2_data, expand.grid(valence_scale = 0, arousal_scale = xRange2, intervention = xRange3))

# Mixed-effect model (summary printed later)
m_fig2 <- nlme::lme(willingness_scale ~ intervention*valence_scale + intervention*arousal_scale, random = ~ 1 + intervention| sub,
                data = fig2_data)
# Draw graphs
v_results <- AICcmodavg::predictSE(m_fig2, newdata = v_pred)
a_results <- AICcmodavg::predictSE(m_fig2, newdata = a_pred)

v_pred$fit <- v_results$fit
v_pred$se <- v_results$se.fit
a_pred$fit <- a_results$fit
a_pred$se <- a_results$se.fit

arousal_colors <- c("#fc9272", "#de2d26")
valence_colors <- c("#bcbddc", "#756bb1")

fig2a_plot <- ggplot() + 
  # Arousal
  geom_line(data = a_pred, aes(x = arousal_scale, y = fit, color = intervention), size = 2) + 
  geom_ribbon(data = a_pred, aes(x = arousal_scale, ymax = fit + se, ymin = fit - se, fill = intervention), alpha = .1) + 
  scale_x_continuous(name = "Arousal", limits = c(-1.7, 1.7), breaks = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5)) +
  scale_y_continuous(name = "Willingness", limits = c(-.4, .1), breaks = c(-0.4, -0.3, -0.2, -0.1, 0, 0.1)) +
  scale_color_manual(values = arousal_colors) + 
  scale_fill_manual(values = arousal_colors) + 
  geom_hline(yintercept = 0, lty = 3) + 
  geom_vline(xintercept = 0, lty = 3) + 
  fig2_theme
fig2a_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig2a.pdf"), plot = fig2a_plot, width = 8, height = 6)
}

fig2b_plot <- ggplot() + 
  # Valence
  geom_line(data = v_pred, aes(x = valence_scale, y = fit, color = intervention), size = 2) + 
  geom_ribbon(data = v_pred, aes(x = valence_scale, ymax = fit + se, ymin = fit - se, fill = intervention), alpha = .1) + 
  scale_x_continuous(name = "Valence", limits = c(-1.7, 1.7), breaks = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5)) +
  scale_y_continuous(name = "Willingness", limits = c(-.4, .1), breaks = c(-0.4, -0.3, -0.2, -0.1, 0, 0.1)) +
  scale_color_manual(values = valence_colors) + 
  scale_fill_manual(values = valence_colors) + 
  geom_hline(yintercept = 0, lty = 3) + 
  geom_vline(xintercept = 0, lty = 3) + 
  fig2_theme
fig2b_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig2b.pdf"), plot = fig2b_plot, width = 8, height = 6)
}

# Willngness model
broom.mixed::tidy(m_fig2, effect = "fixed") %>%
  mutate(
    p.value = format(round(p.value, digits=3), nsmall = 3),
    p.label = case_when(p.value <= .001 ~ "***", 
                        p.value <= .01 ~ "**", 
                        p.value <= .05 ~ "*", 
                        p.value > .05 ~ "n.s."),
    p.value = cell_spec(p.value,
                        "html",
                        color = "white", 
                        background = if_else(p.value < 0.05, "red", "black")),
    p.label = cell_spec(p.label,
                        "html",
                        color = "white", 
                        background = if_else(p.label != "n.s.", "red", "black"))
  ) %>%
  kable(format = "html", 
        caption = "Willingness Model ", 
        escape = FALSE) %>% # escape = FALSE critical to avoid escaping special characters in the HTML
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  footnote(general = "Formula: willingness_scale ~ intervention * valence_scale + intervention * arousal_scale + (1 + intervention|sub)\n Intervention reference category is fear")

# Simple effects - change reference category
fig2_data_s <- fig2_data %>% mutate(intervention = fct_relevel(intervention, "altruism", "fear"))
m_fig2_s <- nlme::lme(willingness_scale ~ intervention*valence_scale + intervention*arousal_scale, 
                 random = ~ 1 + intervention| sub, data = fig2_data_s)
```

# Figure 3 - Emotional experience predicts reported changes in self-isolation after altruistic intervention
- Figure 3 graph
- Figure 3 descriptives
- Figure 3 statistics

```{r fig3}
# Same dataframe as in Fig 2

# Mixed-effect model (summary printed later)
m_fig3 <- nlme::lme(change_scale ~ intervention*valence_scale + intervention*arousal_scale, random = ~ 1 + intervention| sub,
                data = fig2_data)

v_results <- AICcmodavg::predictSE(m_fig3, newdata = v_pred)
a_results <- AICcmodavg::predictSE(m_fig3, newdata = a_pred)

v_pred$fit <- v_results$fit
v_pred$se <- v_results$se.fit
a_pred$fit <- a_results$fit
a_pred$se <- a_results$se.fit

fig3a_plot <- ggplot() + 
  # Arousal
  geom_line(data = a_pred, aes(x = arousal_scale, y = fit, color = intervention), size = 2) + 
  geom_ribbon(data = a_pred, aes(x = arousal_scale, ymax = fit + se, ymin = fit - se, fill = intervention), alpha = .1) + 
  scale_x_continuous(name = "Arousal", limits = c(-1.7, 1.7), breaks = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5)) +
  scale_y_continuous(name = "Change", limits = c(-.6, .13), breaks = c(-0.6, -0.4, -0.2, 0.0)) +   
  scale_color_manual(values = arousal_colors) + 
  scale_fill_manual(values = arousal_colors) + 
  geom_hline(yintercept = 0, lty = 3) + 
  geom_vline(xintercept = 0, lty = 3) + 
  fig2_theme
fig3a_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig3a.pdf"), plot = fig3a_plot, width = 8, height = 6)
}

fig3b_plot <- ggplot() + 
  # Valence
  geom_line(data = v_pred, aes(x = valence_scale, y = fit, color = intervention), size = 2) + 
  geom_ribbon(data = v_pred, aes(x = valence_scale, ymax = fit + se, ymin = fit - se, fill = intervention), alpha = .1) + 
  scale_x_continuous(name = "Valence", limits = c(-1.7, 1.7), breaks = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5)) +
  scale_y_continuous(name = "Change", limits = c(-.6, .13), breaks = c(-0.6, -0.4, -0.2, 0.0)) +   
  scale_color_manual(values = valence_colors) + 
  scale_fill_manual(values = valence_colors) + 
  geom_hline(yintercept = 0, lty = 3) + 
  geom_vline(xintercept = 0, lty = 3) + 
  fig2_theme
fig3b_plot

if (save_plots == TRUE) {
  ggsave(filename = paste0(dir_graphs, "/fig3a.pdf"), plot = fig3a_plot, width = 8, height = 6)
}

# Change model
broom.mixed::tidy(m_fig3, effect = "fixed") %>%
  mutate(
    p.value = format(round(p.value, digits=3), nsmall = 3),
    p.label = case_when(p.value <= .001 ~ "***", 
                        p.value <= .01 ~ "**", 
                        p.value <= .05 ~ "*", 
                        p.value > .05 ~ "n.s."),
    p.value = cell_spec(p.value,
                        "html",
                        color = "white", 
                        background = if_else(p.value < 0.05, "red", "black")),
    p.label = cell_spec(p.label,
                        "html",
                        color = "white", 
                        background = if_else(p.label != "n.s.", "red", "black"))
  ) %>%
  kable(format = "html", 
        caption = "Change Model ", 
        escape = FALSE) %>% # escape = FALSE critical to avoid escaping special characters in the HTML
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  footnote(general = "Formula: change_scale ~ intervention*valence_scale + intervention*arousal_scale + (1 + intervention|sub)\n Intervention reference category is fear")

# Simple effects - change reference category
fig3_data_s <- fig2_data %>% mutate(intervention = fct_relevel(intervention, "altruism", "fear"))
m_fig3_s <- nlme::lme(change_scale ~ intervention*valence_scale + intervention*arousal_scale, 
                 random = ~ 1 + intervention| sub, data = fig3_data_s)
```

# Session Info
```{r session_info}
sessionInfo()
```

# Appendix
Code used for all figures and analyses. 

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```
